Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-02 papers/BON_VHDL/paper.tex
Appendix

%======================================================================
\section{Introduction}
The \STs, represents heterogeneous collection of digital, analog 
and mixed signal hardware components. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STs simulator. 
The development of complex system requires sophisticated tool and methodology 
in order to be able to complete a correct design in time.  
This article describes a refinement method from BON to VHDL-AMS
The authors will illustrate in this paper how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from BON to VHDL-AMS. As an extremly simple example, 
we will give practical aspect of refinement from BON to VHDL-AMS,
applied on A/D convertor, in order to produce formal specification 
and software simulation.
%=====================================================================

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Mapping between BON and VHDL-AMS}
\subsection{Static model mapping}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
\subsection{Operators-expressions mapping}
%\todo{dragan 27/07/2009 - Figure out :  VHDL-ASM as BON  represents an strongly typed language.}
This subsection summarises all relations on expressions - operators between VHDL-AMS and BON.
\input{operators}

\subsection{Type mapping}

@@

An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The textual 
presentation of \ent is shown in Figure.1. 
\input{adc-entity}

@@

%======================================================================
%% \nocite{ex1,ex2}
\bibliographystyle{plain}
\bibliography{extra,%
              abbrev,%
              ads,%
              category,%
              complexity,%
              hypertext,%
              icsr,%
              knowledge,%
              languages,%
              linguistics,%
              meta,%
              metrics,%
              misc,%
              modeling,%
              modeltheory,%
              reuse,%
              rewriting,%
              softeng,%
              specification,%
              ssr,%
              technology,%
              theory,%
              web,%
              upcoming,%
              upcoming_conferences,%
              conferences,%
              workshops,%
              verification,%
              escjava,%
              jml,%
              nijmegen}

@@

>>>>

%======================================================================
\section{Introduction}
The \STs, represents heterogeneous collection of digital, analog 
and mixed signal hardware components. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STs simulator. 
The development of complex system requires sophisticated tool and methodology 
in order to be able to complete a correct design in time.  
The authors will illustrate in this paper how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from VHDL-AMS to BON. As an extremly simple example, 
we will give practical aspect of refinement from VHDL-AMS to BON,
applied on A/D convertor, in order to produce formal specification 
and software simulation. A complete list of the mapping between BON 
and VHDL-AMS can be found in the appendix.
%=====================================================================

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Mapping between BON and VHDL-AMS}

@@

An VHDL-AMS design units are described using an \ent-\arch structure. 
The design unit contains an \ent and one or more \archs. 
The \ent specifies the interface that an entity provides of itself 
to the outside. In other words, \ent introduces a name, list of 
input/output ports and the definition of the generic parameters. 
The textual presentation of \ent is shown in Figure.1. 
\input{adc-entity}

@@

%% \nocite{ex1,ex2}
\bibliographystyle{plain}
\bibliography{extra,%
              abbrev,%
              ads,%
              category,%
              complexity,%
              hypertext,%
              icsr,%
              knowledge,%
              languages,%
              linguistics,%
              meta,%
              metrics,%
              misc,%
              modeling,%
              modeltheory,%
              reuse,%
              rewriting,%
              softeng,%
              specification,%
              ssr,%
              technology,%
              theory,%
              web,%
              upcoming,%
              upcoming_conferences,%
              conferences,%
              workshops,%
              verification,%
              escjava,%
              jml,%
              nijmegen}

@@

%======================================================================
\appendix
\section {APPENDIX}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
%\todo{dragan 27/07/2009 - Figure out :  VHDL-ASM as BON  represents an strongly typed language.}
\input{operators}
%======================================================================

### 2009-08-02 papers/BON_VHDL/static.tex
Appendix

\begin{center}
    \begin{tabular}{|l|l|l|}
    	\hline
    	VHDL-AMS & BON & Description \\ \hline
    	\ducs (packages) & \Sc & 
	\begin{minipage}[c]{7cm} 
                 \vskip 3mm
    		VHDL-AMS allows hierarchical structure modeling, 
    		meaning that subsistems (\ducs), can be developed independently.
    		As an top-level description (informal/formal), \Sc connect all the \ducs
    		together to a complete design. Actually \Sc can be understood 
                as VHDL-AMS package as a way of grouping a collection of related 
                declarations that serve a common purpose.
                \\ 
    	\end{minipage}\\ \hline
        \duc & \Clc &
	\begin{minipage}[c]{7cm} 
                \vskip 3mm
		An  subsistem which represent \duc.
                \\ 
    	\end{minipage}\\ \hline
	 \du & \Csc &
	\begin{minipage}[c]{7cm}
	      \vskip 3mm	 
              \Csc  describes \du. It can be identify with the primary unit (\ent) and secondary 
	      unit (\arch) structure in VHDL-AMS.
	      The \Csc's name corresponds to the name of the entity in VHDL-AMS.
              \\
    	\end{minipage}\\ \hline
        \arch & \Ft & 
	\begin{minipage}[c]{7cm} 
              \vskip 3mm
	      The feature section of the \Csc, where the mathematical 
	      transfer function of the component is entered, holds the same information 
	      as the \arch section of the VHDL-AMS.
              \\
    	\end{minipage}\\ \hline

>>>>

\begin{center}
    \begin{tabular}{|c|c|l|}
        \hline
        \multicolumn{3}{|c|}{Static mapping}\\ \hline
    	\hline
    	VHDL-AMS & BON & Description \\ \hline
    	\ducs & \Sc & 
	\begin{minipage}[c]{0.5\linewidth}
                 \vskip 1mm
    		VHDL-AMS allows hierarchical structure modeling, 
    		meaning that subsistems (\ducs), can be developed independently.
    		As an top-level description (informal/formal), \Sc connect all the \ducs
    		together to a complete design. Actually \Sc can be understood 
                as VHDL-AMS package as a way of grouping a collection of related 
                declarations that serve a common purpose.

    	\end{minipage}\\ \hline
        \duc & \Clc &
	\begin{minipage}[c]{0.5\linewidth} 
                \vskip 1mm
		An  subsistem which represent \duc.

    	\end{minipage}\\ \hline
	 \du & \Csc &
	\begin{minipage}[c]{0.5\linewidth}
	      \vskip 1mm	 
              \Csc  describes \du. It can be identify with the primary unit (\ent) and secondary 
	      unit (\arch) structure in VHDL-AMS.
	      The \Csc's name corresponds to the name of the entity in VHDL-AMS.

    	\end{minipage}\\ \hline
        \arch & \Ft & 
	\begin{minipage}[c]{0.5\linewidth} 
              \vskip 1mm
	      The feature section of the \Csc, where the mathematical 
	      transfer function of the component is entered, holds the same information 
	      as the \arch section of the VHDL-AMS.    
    	\end{minipage}\\ \hline
